Search for Spatially Extended Fermi-LAT Sources Using Two Years of Flight Data

### 2011-08-12 extended_catalog/paper/extended_catalog.tex
better table

% some units
\newcommand{\kev}{\text{Kev}\xspace}
\newcommand{\mev}{\text{MeV}\xspace}
\newcommand{\gev}{\text{GeV}\xspace}
\newcommand{\tev}{\text{TeV}\xspace}
\newcommand{\sr}{\text{sr}\xspace}
\newcommand{\s}{\text{s}\xspace}
\newcommand{\ph}{\text{ph}\xspace}
\newcommand{\cm}{\text{cm}\xspace}
\renewcommand{\sec}{\text{s}\xspace}
\newcommand{\tsext}{{\ensuremath{\text{TS}_{\text{ext}}}}\xspace}
\newcommand{\tsinc}{\ensuremath{\text{TS}_{\text{inc}}}\xspace}
\newcommand{\loglikelihood}{\ensuremath{LL}\xspace}

@@

@@

We tested two different models for the
spatial shape, either a two dimensional Gaussian
\begin{equation}\label{gauss_pdf}
  I(x,y)=\tfrac{1}{2\pi\sigma^2}\exp\left(-(x^2+y^2)/2\sigma^2\right)
\end{equation}
or a uniform disk
\begin{equation}\label{disk_pdf}
  I(x,y)=
  \begin{cases}
    \frac{1}{\pi\sigma^2} & x^2+y^2\le\sigma^2 \\
    0                      & x^2+y^2>\sigma^2
  \end{cases}
\end{equation}
Although these shapes are significantly different, the convolution
of them with the PSF look similar.  Figure~\ref{compare_disk_gauss}
demonstrates this by showing $I_\text{src}$, the PSF, and the PDF for
a radially symmetric uniform and Gaussian surface brightness of size 0.5\deg.\footnote{To
allow a valid comparison between Gaussian and disk shaped morphologies,
we define the source size for this test as the radius containing
68\% of the intensity ($\rsixeight$).  $\rsixeight_\text{,Gaussian}=1.51\sigma$
and $\rsixeight_\text{,disk}=0.82\sigma$ where $\sigma$
is defined in equation~\ref{gauss_pdf} and
equation~\ref{disk_pdf} respectively.} This plot shows that we are
not very sensitive to probing the exact structure of an extended source.
In the search for extended sources, we therefore use only a uniform
disk as our spatial extension shape. We then quote the radius of the
disk edge as the size of the source.

@@

Two nearby galaxies the Large Magalenic Cloud and the Small Magalenic
Cloud were included in 2FGL (\cite{lmc,smc}).  They were significantly
detected using 1-100 \gev photons. Our
fit extension is comparable to the published result, but we note that
previous publication used a more complicated double Gaussian spatial
model when fitting the LMC.

@@

% failed to detect vela x + cen a
Our analysis was unable to resolve Vela X which would have required first
removing the pulsed photons from the Vela pulsar. This is beyond the
scope of this paper.  Our analysis also failed to detect a significant
extension for the Centaurus A Lobes (\cite{cen_a_lat}). This is because
the source's emission is significantly different from a uniform
radially symmetric Disk.

@@

The region also has abundant molecular and atomic gas traced by CO
and HI but also plenty of dark gas, the kind that we find only by its
association with dust emission. Embedded star-forming regions make it even
more challenging to measure the column density of dust.  Although this
region is significantly extended, we conclude that this source most
likely represents inadequacy in the diffuse $\gamma$-ray emission model.

\todo[inline]{Can we get another citation about dark gas and stuff?
And a better description of spectral index being typical of diffuse emission.
Stefan says that Markus should write this section.
He also says we should cite (\cite{isabelle_dark_gass}).  
}

@@

2FGL\,J1615.2-5138 is spatially coincident with the extended
\tev source HESS\,J1616-508 (\cite{hess_plane_survey}).  In
figure~\ref{1FGL_J1613.6-5100c}, contours of HESS\,J1616-508 are overlaid
on 2FGL\,J1615.0-5051.  The H.E.S.S. experiment measured a Gaussian
extension $0.136\pm 0.008$ when fitting the source with an elliptical
Gaussian surface brightness.  This size corresponds to a 68\% containment
radius of $\rsixeight=0.21\deg\pm0.01\deg$. This size is comparable to the LAT
size $\rsixeight=0.27\deg\pm0.03\deg$ (see section~\ref{compare_source_size}).
Figure~\ref{hess_seds} shows that the LAT spectrum of 2FGL\,J1615.0-5051
connects smoothly to the H.E.S.S spectrum of HESS\,J1616-508.

HESS\,J1616-508 is located in the region of two SNRs, RCW103 (G332.4-04)
and Kes 32 (G332.4+0.1) but is not spatially coincident with either
of them.  HESS\,J1616-508 is near three pulsars near PSR J1614-5048,
PSR J1616-5109, and PSR J1617-5055 but only PSR J1617-5055 only
PSR J1617-5055 is energetically favored as being the \tev emitter
(\cite{integral_HESS_J1616-508}).  \cite{hess_plane_survey}
speculated that this young pulsar could be responsible for the
emission of HESS\,J1616-508.  HESS\,J1616-508 is 9' away from PSR
J1617-5055, which was discovered during ASCA observations of RCW 103
(\cite{discovery_of_PSR_J1617-5055}). Using an outer gap magnetospheric
pulsar model, it was previously predicted to be a \tev emitter
(\cite{pulsar_tev_emission_predictions}).

The pulsar's position is offset from the maximum of the H.E.S.S
emission and would require an asymetric PWNe to power the \tev
emission. Offset PWN are expected on theoretical grounds due
to the PWNe being crushed by an asymmetric SNR reverse shock
(\cite{offset_pwn_ahronian,offset_pwn_blondin}) but this makes a
possible association more difficult.  For HESS\,J1825-137, the X-ray
emission is directed along the \tev offset making this association more
compelling.\cite{hess_j1825_hess}.

In the region around HESS\,J1616-508, Suzaku found only an upper limit
in the 2-10 \kev energy range and suggested this source as an example
of a ``dark particle accelerator'' (\cite{suzakzu_HESS_J1616-508}).
\cite{integral_HESS_J1616-508} found no evidence of hard X-ray emission
in the region of HESS\,J1616-508 in the 20-100 \kev energy band with the
IBIS/ISGRBI on board INTEGRAL. They also observed the field with the XRT
on board {\em Swift} between 0.2-10 \kev and found no compelling source
counterpart. Using archival XMM-Newton and BeppoSAX data, they found no
plausible X-ray counterpart except for PSR J1617-5055.

Finally, Chandra ACIS observations of PSR J1617-5055 revealed
an underlomonous PWN $\approx1'$ in size around the pulsar
(\cite{discovery_of_pwn_for_PSR_J1617-5055}). But the PWN is not
assymetric towards HESS\,J1616-508 which casts doubt upon the association.

\todo[inline]{
Note about how it is difficult to explain the TeV to X-ray emission
ratio b/c of magnetic field. Refernece in page 7 of (sukazu paper on HESS J1614-518, but
it also refers to (Matsumoto et. al 2007 and says this requires small b/field with strong
cutoff in eletron energy). Also some not eabout different photon fields
being possible.}

\todo[inline]{
Note about this this paper finds other stuff: (\cite{discovery_of_pwn_for_PSR_J1617-5055}).
}

\todo[inline]{
The \gev emission is suggested to be the same emission component as
the \tev emission, but further observations of this source at other
frequencies will likely be needed to firmly associated this source.
}

\todo[inline]{Finish interpretations of HESS\,J1616-508.}

@@

This source is currently unidentifed. There are five nearby pulsars,
but note are luminous enough to provide the required energy output
to power the \tev emission (\cite{closer_look_hess_j1614-518}).

HESS J1614-518 is spatially coincident with a young open cluster Pismis
22 (\cite{hess_1614_landi_atel,closer_look_hess_j1614-518}).
\gev and \tev emission could arrise from
hadronic acceleration in the winds of massive stars
\cite{cosmic_rays_and_gamma-rays_from_ob_stars,gamma-ray_production_in_young_open_clusters}.
Pisim 22 is at a distance $\approx1$ kpc and can energetically account
for the \tev emission (\cite{closer_look_hess_j1614-518}), but
it is difficult to explain the difference in size and positional offset
between Pismis 22 and HESS\,J1614-518.

@@

This extended source is spatially coincident with the extended
\tev source HESS\,J1632-478 (\cite{hess_plane_survey}).  In
figure~\ref{1FGL_J1632.9-4802c}, contours of  HESS\,J1632-478 are
overlaid on 2FGL\,J1635.4-4717c.  H.E.S.S measured a Gaussian extension of
$\sigma=0.21\pm0.05$ and $0.06\pm0.04$ along the semi-major and semi-minor
axes when fitting the source with an elliptical Gaussian surface 
brightness.
This corresponds to a 68\% containment size $\rsixeight=0.31\deg\pm0.08\deg$
and $0.09\pm0.06$ along the semi-major and semi-minor axis. This
size is consistent with the LAT size $\rsixeight=0.36\deg\pm0.04\deg$.
Figure~\ref{hess_seds} shows that the LAT spectrum of 2FGL\,J1635.4-4717c
connects smoothly to the H.E.S.S spectrum of HESS\,J1632-478 and most
likely corresponds to the same emission process.

\cite{hess_plane_survey} argued that this source is positionally
coincident with the hard X-ray source IGR\,J1632-4751 discovered above
15 \kev by the INTEGRAL satellite (\cite{Igr_J16320-4751_circ}).
It was also observed by XMM-Newton between 2 and 10 \kev
(\cite{xmm_newton_IGR_J16320-4751}) and ASCI between 0.7 and 10 \kev
(\cite{asca_plane_survey}).  But this X-ray source is suspected to be
an galactic X-Ray Binary so the \gev and \tev extension HESS\,J1632-478
and 2FGL\,J1632.4-4753c disfavors the association.

Further observations of the region around HESS\,J1632-478 by XMM-Newton
reveal extended emission between 0.2 \kev and 15 \kev with an elliptical
size of $\approx32''$ and $\approx15''$ in the semi-major and semi-minor
axes and inside this extended emission was point-like emission
(\cite{hess_j1632_478_xmm_newton}).  This x-ray source is positionally
coincident with the \tev centroid of the H.E.S.S source.  In addition,
they used data from MGPS-2, an 843 MHz survey of the galactic plane
carried out with the Molonglo Observatory Synthesis Telescope (MOST)
to detect an extended diffuse radio source whose size matches well the
extended X-ray emission \cite{most_survey_galactic_plane}.

They argued that the positional match between the radio and X-ray
observations argues for a single synchrotron processes emitting from
radio to X-ray.  This same source could be responsible for the \tev
emission due to inverse Compton and this matches the expected emission
from a typical PWNe.

The increased \gev and \tev size compared to the X-ray size
has previously been observed in several aging PWNe including 
HESS\,J1825-137 (\cite{hess_j1825_xmm_newton,hess_j1825_hess}, HESS\,J1640-465
(\cite{hess_plane_survey,xmm_newton_hess_j_1640-466}),
and Vela X (\cite{vela_x_rosat,vela_x_hess}). 
This can be explained by a different synchrotron cooling
time for the electroncs producing X-rays and \tev gamma rays.
Because of the spectral and spatial match between the \gev and \tev
emission, the LAT data naturally fits into this model as being the rising
edge of the inverse Compton component of a PWN.

@@

This source is spatially coincident with the \tev
source HESS\,J1837-069 (\cite{hess_plane_survey}).  In
figure~\ref{1FGL_J1837.5-0659c}, contours of HESS\,J1837-069
are overlaid on 2FGL\,J1837.3-0700c. H.E.S.S. measured a 
Gaussian extension
of $\sigma=0.12\pm0.02$ and $0.05\pm0.02$ along the semi-major and
semi-minor axis when fitting the source with an elliptical Gaussian
surface brightness.  This corresponds to a 68\% containment radius of
$\rsixeight=0.18\deg\pm0.03\deg$ and $0.08\deg\pm0.03\deg$ along the semi-major
and semi-minor axis. The size is comparable to LAT which fit a 68\%
containment radius of $\rsixeight=0.29\deg\pm0.07\deg$.  The LAT size is larger
than the H.E.S.S. size but the sizes are almost almost within the
$1\sigma$ errors. Figure~\ref{hess_seds} shows that the LAT spectrum
of 2FGL\,J1837.3-0700c connects smoothly to the H.E.S.S spectrum of
HESS\,J1837-069.

\todo[inline]{Add interpretation of HESS\,J1837-069.}

@@

Figure~\ref{compare_index_2FGL} shows a comparison of the spectral index
of LAT detected extended sources and of all sources in 2FGL. This, and
table~\ref{known_extended_sources} and~\ref{new_ext_srcs_table},
show that the LAT observes a population of hard (index $<2$)
extended sources above 10 \gev which connects to \tev sources.
Figure~\ref{hess_seds} shows the LAT energy spectrum of four of the
extended sources which were first discovered in the H.E.S.S. Galactic
plane survey (\cite{hess_plane_survey}) and have a matching size to LAT
extended sources.  The LAT energy spectrum connects smoothly to \tev.
This is also true of HESS\,J1825-137 (\ref{fermi_hess_j1825}) and RX
J1713.7-3946 (\cite{rx_j1713_lat}). We conclude that the \gev and \tev
emission from these sources is coming from the same emission mechanism.

For the LAT extended sources also seen in \tev,
figure~\ref{gev_vs_tev_plot} shows a comparison of their sizes.  There is
a good correlation between the \gev and \tev sizes of the sources. Even
so, the size of PWNe are expected to vary across the \gev and \tev energy
range and the size of HESS\,J1825-137 was seen by H.E.S.S. to vary
between 200 \gev and 20 \tev (\cite{energy_dependent_hess_j1825}).
HESS\,J1825-137 is significantly larger in \gev than \tev
(\cite{fermi_hess_j1825}).  It is interesting to compare the \gev and
\tev size of other PWN candidates, but definitively measuring this effect
would require a more careful analysis of the LAT data using the same 
elliptical surface brightness model.

Figure~\ref{gev_vs_tev_histogram} compares the size of the 21 extended
LAT sources to the 42 extended H.E.S.S. sources.  Because of the large
field of view and all sky coverage, the LAT can more easily measure
larger sources including the LMC and SMC.  On the other hand, the
smaller angular resolution of Air Cherenkov detectors allows them to
measure a population of extended sources below our sensitivity limit
(currently at about $\approx0.2\deg$).  Fermi has a five year nominal
livetime with a goal of ten years of operation. With increased exposure,
the LAT will likely begin to resolving these smaller \tev sources.
As figure~\ref{time_sensitivity} showed, our sensitivity to these smaller
sources will actually improve faster than $\sqrt{t}$.

@@

\clearpage
\begin{figure}
  \begin{center}
    \includegraphics{ic443_plots/four_plots_ic443.pdf}
    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/four_plots_ic443/v1/run.py
    \caption{
    All plots are for the SNR IC443 using two years of data.
    % ts vs extension
    Plot (a) is the change in \ts when varying the
    extension of the source.  
    % ts_ext vs energy
    Plot (b) is \tsext in twelve energy bins. This plot shows that there is
    little gain in sensitivity to the extension using photons
    with energies below 1 \gev, even for a source with an index $\approx2.4$.
    % radial integral
    Plot (c) is the sum of all counts within a given radial distance
    from the source binned uniformly in $\theta^2$. 
    Overlaid on the plot is the model predicted counts assuming that
    the source is both an extended source and a point source
    % smoothed counts
    Plot (d) is a counts map of the source with the Galactic and
    isotropic diffuse emission subtracted and smoothed by a $0.1\deg$
    Gaussian kernel.  The inset is the predicted emission from a point
    source of the same spectrum and intensity.  The PSF is smoothed
    by the same kernel.  Plots (a), (c), and (d) use only 1-100 \gev photons. 
    Plots (c) and (d)
    use only photons which converted in the front
    part of the detector and have an improved angular resolution.
    }
    \label{four_plots_ic443}
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics{mc_plots/compare_disk_gauss.pdf}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_disk_gauss/v2/compare_disk_gauss.pdf
    \end{center}
    \caption{
    A comparison of the Gaussian and uniform disk PDFs before and
    after convolving with the PSF.  The black line is the PSF that
    would be observed for a power-law source of spectral index 2. The
    dashed red line is the probability density of a Gaussian with
    $\rsixeight=0.5\deg$, which is just a straight line on this plot.
    The dashed blue line is the probability density for a uniform disk
    with $\rsixeight=0.5\deg$.  Finally, the solid red and blue lines
    show the convolution of the Gaussian and uniform disk with the PSF.
    Plot (a) uses a 1-100 \gev energy range while plot (b)
    uses a 10-100 \gev enregy range. This plot demonstrates that different
    surface brightness models when smoothed by the PSF look similar.  The $y$
    axis is the log of the intensity and the $x$ axis is $\theta^2$.
    This plot is discussed further in section~\ref{compare_source_size}.
    }\label{compare_disk_gauss}
  \end{figure}

    \begin{table}
  \begin{centering}
    \begin{tabular}{ r | r | r | r }
      \hline
      \hline
      $\gamma$ & flux ($\ph/\cm^2/\sec$) & $N_\text{sims}$ & $\langle\ts\rangle$ \\
      \hline
      1.5 &          $10^{-6}$ &           31952 &  92862 \\
      &  $3\times 10^{-7}$ &           31962 &  22169 \\
      &          $10^{-7}$ &           31977 &   5806 \\
      &  $3\times 10^{-8}$ &           31991 &   1270 \\
      &          $10^{-8}$ &           31940 &    301 \\
      &  $3\times 10^{-9}$ &           30324 &     62 \\
      \hline
      2 &          $10^{-6}$ &           31872 &  22067 \\
      &  $3\times 10^{-7}$ &           31890 &   4898 \\
      &          $10^{-7}$ &           31858 &   1097 \\
      &  $3\times 10^{-8}$ &           31632 &    236 \\
      &          $10^{-8}$ &           27491 &    103 \\
      \hline
      2.5 &          $10^{-6}$ &           31822 &   4706 \\
      &  $3\times 10^{-7}$ &           31822 &    889 \\
      &          $10^{-7}$ &           31169 &    176 \\
      &  $3\times 10^{-8}$ &           21591 &     41 \\
      \hline                                                
      3 &          $10^{-6}$ &           31763 &    929 \\
      &  $3\times 10^{-7}$ &           31665 &    161 \\
      &          $10^{-7}$ &           19271 &     40 \\
      \hline
    \end{tabular}
    \caption{
    This table presents a list of the spectral models (flux and
    spectral index) used in the Monte Carlo study of \pointlike
    described in section~\ref{monte_carlo_validation} and presented
    in figure~\ref{ts_ext_mc}.  For each spectral model, the number of
    statistically independent simulations and the average value of \ts
    value ($\langle\ts\rangle$) is tabulated.  The Monte Carlo simulation
    spans parameters representative of sources that could be detected
    by the LAT.  The simulation is of spectral indices $\gamma$ of 1.5,
    2, 2.5, and 3.  The simulation is of fluxes varying from a $5\sigma$
    source detection to a $>10\sigma$ source detection.  Only simulations
    which produced statistically significant detections ($\ts>25$)
    were kept.  What is quoted is the $>100$ \mev integral flux measured
    in units of $\ph/\cm^2/\sec$.  More information about this Monte
    Carlo analysis is presented in section~\ref{monte_carlo_validation}.
    }\label{ts_ext_num_sims}
  \end{centering}
\end{table}

>>>>

% some units
\newcommand{\kev}{\text{Kev}\xspace}
\newcommand{\mev}{\text{MeV}\xspace}
\newcommand{\gev}{\text{GeV}\xspace}
\newcommand{\tev}{\text{TeV}\xspace}
\newcommand{\sr}{\text{sr}\xspace}
\newcommand{\s}{\text{s}\xspace}
\newcommand{\ph}{\text{ph}\xspace}
\newcommand{\cm}{\text{cm}\xspace}
\renewcommand{\sec}{\text{s}\xspace}
\newcommand{\tsext}{{\ensuremath{\text{TS}_{\text{ext}}}}\xspace}
\newcommand{\tsinc}{\ensuremath{\text{TS}_{\text{inc}}}\xspace}
\newcommand{\loglikelihood}{\ensuremath{LL}\xspace}
\newcommand{\chandra}{\text{{\em Chandra}}\xspace}

@@

\todo[inline]{add note about how high energy emission may be hadron,
and the origin of cosmic rays}

@@

We tested two different models for the
surface brightness profile, either a two dimensional Gaussian
\begin{equation}\label{gauss_pdf}
  I(x,y)=\tfrac{1}{2\pi\sigma^2}\exp\left(-(x^2+y^2)/2\sigma^2\right)
\end{equation}
or a uniform disk
\begin{equation}\label{disk_pdf}
  I(x,y)=
  \begin{cases}
    \frac{1}{\pi\sigma^2} & x^2+y^2\le\sigma^2 \\
    0                      & x^2+y^2>\sigma^2
  \end{cases}
\end{equation}
Although these shapes are significantly different, the convolution
of them with the PSF look similar.  Figure~\ref{compare_disk_gauss}
demonstrates this by showing $I_\text{src}$, the PSF, and the PDF for
a radially symmetric uniform brightness and the Gaussian surface brightness of size 0.5\deg.\footnote{To
allow a valid comparison between Gaussian and disk shaped morphologies,
we define the source size for this test as the radius containing
68\% of the intensity ($\rsixeight$).  $\rsixeight_\text{,Gaussian}=1.51\sigma$
and $\rsixeight_\text{,disk}=0.82\sigma$ where $\sigma$
is defined in equation~\ref{gauss_pdf} and
equation~\ref{disk_pdf} respectively.} This plot shows that we are
not very sensitive to probing the exact structure of an extended source.
In the search for extended sources, we therefore use only a uniform
disk as our spatial extension shape. We then quote the radius of the
disk edge as the size of the source.

@@

Two nearby galaxies the Large Magalenic Cloud and the Small Magalenic
Cloud were included in 2FGL (\cite{lmc,smc}).  They were significantly
detected using 1-100 \gev photons. Our
fit extension is comparable to the published result, but we note that
previous publication used a more complicated two Gaussian surface
brightness spatial model when fitting the LMC.

@@

% failed to detect vela x + cen a
Our analysis was unable to resolve Vela X which would have required first
removing the pulsed photons from the Vela pulsar. This is beyond the
scope of this paper.  Our analysis also failed to detect a significant
extension for the Centaurus A Lobes (\cite{cen_a_lat}). This is because
the source's emission is significantly different from a uniform
radially symmetric surface brightness.

@@

The region also has abundant molecular and atomic gas traced by CO
and HI but also plenty of dark gas, the kind that we find only by its
association with dust emission (\cite{isabelle_dark_gass}). Embedded
star-forming regions make it even more challenging to measure the column
density of dust.  Therefore this source might represent an inadequacy
in the diffuse $\gamma$-ray model

@@

2FGL\,J1615.2-5138 is spatially coincident with the extended
\tev source HESS\,J1616-508 (\cite{hess_plane_survey}).  In
figure~\ref{1FGL_J1613.6-5100c}, contours of HESS\,J1616-508 are overlaid
on 2FGL\,J1615.0-5051.  The H.E.S.S. experiment measured an
extension $0.136\pm 0.008$ when fitting the source with an elliptical
Gaussian surface brightness.  This size corresponds to a 68\% containment
radius of $\rsixeight=0.21\deg\pm0.01\deg$. This size is comparable to the LAT
size $\rsixeight=0.27\deg\pm0.03\deg$ (see section~\ref{compare_source_size}).
Figure~\ref{hess_seds} shows that the LAT spectrum of 2FGL\,J1615.0-5051
connects smoothly to the H.E.S.S spectrum of HESS\,J1616-508.

HESS\,J1616-508 is located in the region of two SNRs, RCW103
(G332.4-04) and Kes 32 (G332.4+0.1) but is not spatially coincident
with either of them (\cite{hess_plane_survey}).  HESS\,J1616-508 is near
three pulsars PSR J1614-5048, PSR J1616-5109, and PSR J1617-5055
but only PSR J1617-5055 is energetically favored as being the \tev
emitter (\cite{discovery_of_PSR_J1617-5055,integral_HESS_J1616-508}).
\cite{hess_plane_survey} speculated that a PWN powered by this young
pulsar could be responsible for the emission of HESS\,J1616-508.
Because HESS\,J1616-508 is 9' away from PSR J1617-5055, this would
require an assymetric X-ray PWNe to power the \tev emission. However,
\chandra ACIS observations revealed only an underluminous PWN of
about $\approx1'$ size around the pulsar which was not oriented
towards the \tev emission, rendering this association as uncertain
\cite{discovery_of_pwn_for_PSR_J1617-5055}.  No other promising
counterparts were observed in observations of x-ray and soft gamma-ray
emission by Suzaku (\cite{suzakzu_HESS_J1616-508}), Swift/XRT,
IBIS/ISGRBI, BeppoSAX and XMM-Newton (\cite{integral_HESS_J1616-508}).
Finally, \cite{discovery_of_pwn_for_PSR_J1617-5055} found diffuse
emission towards the center of HESS\,J1616-508 using archival radio and
infared observations.  Deeper observations will likely be necessary to
understand this region.

@@

There are five nearby pulsars, but none are luminous enough to
provide the required energy output to power the \gev and \tev emission
(\cite{closer_look_hess_j1614-518}).

HESS\,J1614-518 is spatially coincident with a young open cluster Pismis
22 (\cite{hess_1614_landi_atel,closer_look_hess_j1614-518}).
\gev and \tev emission could arise from
hadronic acceleration in the winds of massive stars
\cite{cosmic_rays_and_gamma-rays_from_ob_stars,gamma-ray_production_in_young_open_clusters}.
Pisim 22 is at a distance $\approx1$ kpc and can energetically account
for the \tev emission (\cite{closer_look_hess_j1614-518}), but
it is difficult to explain the difference in size and positional offset
between Pismis 22 and HESS\,J1614-518.

@@

This extended source is spatially coincident with the extended
\tev source HESS\,J1632-478 (\cite{hess_plane_survey}).
In figure~\ref{1FGL_J1632.9-4802c}, contours of  HESS\,J1632-478
are overlaid on 2FGL\,J1635.4-4717c.  H.E.S.S measured a 
extension of $\sigma=0.21\pm0.05$ and $0.06\pm0.04$ along the
semi-major and semi-minor axes when fitting the source with an
elliptical Gaussian surface brightness.  This corresponds to a 68\%
containment size $\rsixeight=0.31\deg\pm0.08\deg$ and $0.09\pm0.06$
along the semi-major and semi-minor axis. This size is consistent with
the LAT size $\rsixeight=0.36\deg\pm0.04\deg$.  Figure~\ref{hess_seds}
shows that the LAT spectrum of 2FGL\,J1635.4-4717c connects smoothly to
the H.E.S.S spectrum of HESS\,J1632-478.

\cite{hess_plane_survey} argued that HESS\,J1632-478 is
positionally coincident with the hard X-ray source IGR\,J1632-4751
observed by INTEGRAL (\cite{Igr_J16320-4751_circ}), XMM-Newton
(\cite{xmm_newton_IGR_J16320-4751}), and ASCI (\cite{asca_plane_survey}).
But it is suspected to be an galactic X-Ray Binary so the \gev and \tev
extension disfavors the association.

Further observations by XMM-Newton reveal extended emission of size
$\approx32''x\approx15''$ and inside point-like emission coincident with
the peak H.E.S.S. emimssion (\cite{hess_j1632_478_xmm_newton}).  They
found in archival MGPS-2 data a spatially coincident extended radio source
\cite{most_survey_galactic_plane}.  The positional match argues for a
single synchrotron processes producing X-ray and \gev and \tev radiation,
likely due to a PWNe.  The increased \gev and \tev size compared
to the X-ray size has previously been observed in several aging PWNe
including HESS\,J1825-137 (\cite{hess_j1825_xmm_newton,hess_j1825_hess},
HESS\,J1640-465 (\cite{hess_plane_survey,xmm_newton_hess_j_1640-466}),
and Vela X (\cite{vela_x_rosat,vela_x_hess}).  This can be explained by
a different synchrotron cooling time for the electrons producing X-rays
and \tev gamma rays.

@@

This source is spatially coincident with the \tev source HESS\,J1837-069
(\cite{hess_plane_survey}).  In figure~\ref{1FGL_J1837.5-0659c}, contours
of HESS\,J1837-069 are overlaid on 2FGL\,J1837.3-0700c. H.E.S.S. measured
an extension of $\sigma=0.12\pm0.02$ and $0.05\pm0.02$
along the semi-major and semi-minor axis when fitting the source
with an elliptical Gaussian surface brightness.  This corresponds
to a 68\% containment radius of $\rsixeight=0.18\deg\pm0.03\deg$ and
$0.08\deg\pm0.03\deg$ along the semi-major and semi-minor axis. The
size is comparable to LAT which fit a 68\% containment radius of
$\rsixeight=0.29\deg\pm0.07\deg$.  the size difference is not significant
(less than 2 sigma).  Figure~\ref{hess_seds} shows that the LAT spectrum
connects smoothly to the H.E.S.S spectrum of HESS\,J1837-069.

HESS\,J1837-069 is coincident with the hard
and steady X-ray source AX J1838.0-0655
(\cite{einstein_galactic_plane_survey,hard_x-ray_asca,integral_AX_J1838.0-0655,swift_follow_up,pulsations_HESS_J1837-069,suzaku_HESS_J1837-069}).
This source was discovery by RXTE to 
be a pulsar 
sufficiently luminous to power the \tev emission.
AX J1838.0-0655 was spatially resolved by \chandra to be a bright point source
surrounded by a $\sim2'$ nebula (\cite{pulsations_HESS_J1837-069}).

A second X-ray point source AX J1837.3-0652 is in the region of HESS\,J1837-069
(\cite{hard_x-ray_asca,swift_follow_up,pulsations_HESS_J1837-069,suzaku_HESS_J1837-069}).
It was also resolved into point-like and diffuse component
although no pulsations have yet been detected from it
(\cite{pulsations_HESS_J1837-069}).  If AX J1838.0-0655 is a pulsar/PWN
powering HESS\,J1837-069, some of the \tev emission
may also be powered by AX J1837.3-0652.

@@

Figure~\ref{compare_index_2FGL} shows a comparison of the spectral index
of LAT detected extended sources and of all sources in 2FGL. This, and
table~\ref{known_extended_sources} and~\ref{new_ext_srcs_table},
show that the LAT observes a population of hard (index $<2$)
extended sources above 10 \gev which connects to \tev sources.
Figure~\ref{hess_seds} shows the LAT energy spectrum of four of the
extended sources which were first discovered in the H.E.S.S. Galactic
plane survey (\cite{hess_plane_survey}) and have a matching size to LAT
extended sources.  The LAT energy spectrum connects smoothly to \tev.
This is also true of HESS\,J1825-137 (\cite{fermi_hess_j1825}) and RX
J1713.7-3946 (\cite{rx_j1713_lat}).

For the LAT extended sources also seen in \tev,
figure~\ref{gev_vs_tev_plot} shows a comparison of their sizes.  There is
a good correlation between the \gev and \tev sizes of the sources. Even
so, the size of PWNe are expected to vary across the \gev and \tev energy
range and the size of HESS\,J1825-137 was seen by H.E.S.S. to vary
between 200 \gev and 20 \tev (\cite{energy_dependent_hess_j1825}).
HESS\,J1825-137 is significantly larger in \gev than \tev
(\cite{fermi_hess_j1825}).  It is interesting to compare the \gev and
\tev size of other PWN candidates, but definitively measuring this 
would require a more in-depth analysis of the LAT data using the same 
elliptical surface brightness model.

Figure~\ref{gev_vs_tev_histogram} compares the size of the 21 extended
LAT sources to the 42 extended H.E.S.S. sources.  Because of the large
field of view and all sky coverage, the LAT can more easily measure
larger sources including the LMC and SMC.  On the other hand, the smaller
angular resolution of Air Cherenkov detectors allows them to measure a
population of extended sources below our sensitivity limit (currently at
about $\approx0.2\deg$).  Fermi has a five year nominal livetime with a
goal of ten years of operation.  As figure~\ref{time_sensitivity} showes,
our sensitivity to these smaller sources will improve by a factor greater
than $\sqrt{t}$.  With increased exposure, the LAT will likely begin to
resolve these smaller \tev sources.

@@

\clearpage
\begin{figure}
  \begin{center}
    \includegraphics{ic443_plots/four_plots_ic443.pdf}
    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/four_plots_ic443/v1/run.py
    \caption{
    Counts and test statistic profiles for the SNR IC443. (a) \ts
    vs. extension of the source. (b) \tsext for individual energy bands. (c)
    observed radial profile of counts in comparison to the expected profiles
    for a point source (blue) and a spatially extended source (red) . (d)
    smoothed count map after subtraction of the diffuse emission compared
    to the LAT PSF (inset).  Plots (a), (c), and (d) use only 1-100 \gev photons. 
    Plots (c) and (d)
    use only photons which converted in the front
    part of the detector and have an improved angular resolution.
    }
    \label{four_plots_ic443}
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics{mc_plots/compare_disk_gauss.pdf}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_disk_gauss/v2/compare_disk_gauss.pdf
    \end{center}
    \caption{
    A comparison of a Gaussian and disk like surface brightness profile
    of extended sources before and after convolving with the PSF for two
    energy ranges.  The black line is the PSF that would be observed
    for a power-law source of spectral index 2. The dashed red line
    is the brightness profile of a Gaussian with $\rsixeight=0.5\deg$.
    The dashed blue line is the brightness profile for a uniform disk
    with $\rsixeight=0.5\deg$.  The solid red and blue lines show the
    convolution of the Gaussian and uniform disk brightness profiles
    with the LAT PSF.
    }\label{compare_disk_gauss}
  \end{figure}

\begin{deluxetable}{rrrr}
\tabletypesize{\normalsize}
\tablecaption{Monte Carlo Validation Parameters
\label{ts_ext_num_sims}
}
\tablewidth{0pt}
\tablehead{

\colhead{Spectral Index}&
\colhead{Flux\tablenotemark{a}}&
\colhead{$N_\text{sims}$}&
\colhead{$\langle\ts\rangle$}
}

\startdata
      1.5 &          $10^{-6}$ &           31952 &  92862 \\
          &  $3\times 10^{-7}$ &           31962 &  22169 \\
          &          $10^{-7}$ &           31977 &   5806 \\
          &  $3\times 10^{-8}$ &           31991 &   1270 \\
          &          $10^{-8}$ &           31940 &    301 \\
          &  $3\times 10^{-9}$ &           30324 &     62 \\
      \hline
        2 &          $10^{-6}$ &           31872 &  22067 \\
          &  $3\times 10^{-7}$ &           31890 &   4898 \\
          &          $10^{-7}$ &           31858 &   1097 \\
          &  $3\times 10^{-8}$ &           31632 &    236 \\
          &          $10^{-8}$ &           27491 &    103 \\
      \hline
      2.5 &          $10^{-6}$ &           31822 &   4706 \\
          &  $3\times 10^{-7}$ &           31822 &    889 \\
          &          $10^{-7}$ &           31169 &    176 \\
          &  $3\times 10^{-8}$ &           21591 &     41 \\
      \hline                                                
      3   &          $10^{-6}$ &           31763 &    929 \\
          &  $3\times 10^{-7}$ &           31665 &    161 \\
          &          $10^{-7}$ &           19271 &     40 \\
\enddata

\tablenotetext{a}{Integral 1-100 \mev flux in units of $\ph/\cm^2/\sec$}

\tablecomments{
    the spectral models used in the Monte Carlo validation of \pointlike.
    For each model, the number of statistically independent simulations
    and the average value of \ts is tabulated.  The models spans
    representative spectral parameters.
}

\end{deluxetable}
